EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-08-22 draft.tex
Minor reformatting and fix bib warning

% Clarify if they actually achieve that way superlinear improvements - JJ
% They should, in this experiment we only tested the #FEs, but they imply 
% a superlinear improvements as we established in the previous section - Mario

We conclude that superlinear improvements are achievable by selecting an
appropriate configuration consisting of the number of populations, worker
containers, and algorithm selection. Further research should focus on learning
more about how these parameters interact with each other. The BBOB benchmark
results show that the selection and mixing of algorithms can lower the number of
FEs needed to find a solution or find solutions that single algorithms could not
find.

% Probably a final conclusion should be added here, including BBOB
% benchmark and the overall performance - JJ

>>>>

We conclude that superlinear improvements are achievable by selecting an
appropriate configuration consisting of the number of populations, worker
containers, and algorithm combination. Further research should focus on learning
more about how these parameters interact with each other. The BBOB benchmark
results show that the selection and mixing of algorithms can lower the number of
FEs needed to find a solution or find solutions that single algorithms could not
find.
